% ============================================================
% Taiabur Rahman — CV 2026
% Tailored for the French job market (international tech/AI sector)
% Compile with: pdflatex Rahman_CV_2026.tex
% ============================================================
\documentclass[10pt, a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[top=1.4cm, bottom=1.4cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{paracol}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{microtype}
\usepackage{ragged2e}
\usepackage{array}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{dashrule}

% ---- Colours -----------------------------------------------
\definecolor{accent}{RGB}{10, 80, 140}       % Deep professional blue
\definecolor{accentlight}{RGB}{220, 235, 248}
\definecolor{darktext}{RGB}{30, 30, 30}
\definecolor{graytext}{RGB}{100, 100, 100}
\definecolor{rulecol}{RGB}{180, 200, 220}

% ---- Page style --------------------------------------------
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ---- Section headings --------------------------------------
\titleformat{\section}
  {\color{accent}\normalfont\normalsize\bfseries\uppercase}
  {}{0em}{}
  [\vspace{1pt}\color{rulecol}\hrule height 0.6pt\vspace{2pt}]
\titlespacing{\section}{0pt}{7pt}{3pt}

% ---- List style --------------------------------------------
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=0pt,
  topsep=1pt,
  parsep=0pt,
  label=\textcolor{accent}{\textbullet}
}

% ---- Helpers -----------------------------------------------
\newcommand{\jobtitle}[3]{%
  \textbf{#1} \hfill \textcolor{accent}{\small #3}\\
  \textit{\small\color{graytext}#2}%
}
\newcommand{\skill}[2]{\textbf{#1} & \small #2 \\[2pt]}

% ============================================================
\begin{document}
% ============================================================

% ---- HEADER ------------------------------------------------
\begin{center}
  {\fontsize{22pt}{26pt}\selectfont\bfseries\color{darktext} Taiabur Rahman}\\[4pt]
  {\normalsize\color{graytext}
    Machine Learning Engineer \ \textcolor{rulecol}{|} \ Medical Imaging (AI) \ \textcolor{rulecol}{|} \ Fullstack Developer}\\[6pt]
  \small\color{graytext}
  \faMapMarker*\enspace Paris 75019, France
  \enspace\textcolor{rulecol}{\textbar}\enspace
  \faEnvelope\enspace \href{mailto:taiaburbd@gmail.com}{taiaburbd@gmail.com}
  \enspace\textcolor{rulecol}{\textbar}\enspace
  \faPhone\enspace +33\,07\,66\,93\,69\,20
  \\[3pt]
  \faGithub\enspace \href{https://github.com/taiaburbd}{github.com/taiaburbd}
  \enspace\textcolor{rulecol}{\textbar}\enspace
  \faLinkedin\enspace \href{https://www.linkedin.com/in/taiabur-rahman}{linkedin.com/in/taiabur-rahman}
  \enspace\textcolor{rulecol}{\textbar}\enspace
  \faGlobe\enspace \href{https://taiaburbd.github.io}{taiaburbd.github.io}
  \enspace\textcolor{rulecol}{\textbar}\enspace
  \faDesktop\enspace \href{https://ai-miqa.com}{ai-miqa.com}
\end{center}

\vspace{3pt}
{\color{accent}\hrule height 1.2pt}
\vspace{6pt}

% ---- PROFILE SUMMARY (full width) --------------------------
\textbf{\color{accent}Profile — }%
ML Engineer and Medical Imaging specialist with \textbf{4+ years} of fullstack
experience in healthcare SaaS and an \textbf{Erasmus Mundus Master} in Medical Imaging
and Applications (France–Italy–Spain). Research background at \textbf{INSERM Dijon}
in deep learning–based 3D brain segmentation. Proficient in end-to-end pipelines:
data preprocessing, model training (PyTorch, TensorFlow), REST API deployment
(FastAPI, Docker, AWS) and frontend integration (Vue.js, React).
Eager to contribute to R\&D or product teams in French medical-tech or AI sectors.

\vspace{5pt}
{\color{rulecol}\hrule height 0.5pt}
\vspace{4pt}

% ---- TWO-COLUMN LAYOUT -------------------------------------
\columnratio{0.62}
\setlength{\columnsep}{14pt}
\begin{paracol}{2}

% ============================================================
% LEFT COLUMN
% ============================================================

\section{Professional Experience}

\jobtitle{Machine Learning Engineer}{BLACKBIRD.AI — New York, USA (Remote)}{Sept. 2025 – Present}
\begin{itemize}
  \item Developing and improving machine learning models for large-scale data analysis
  \item Contributing to AI system architecture, data pipelines and performance monitoring
  \item Collaborating across engineering and research teams in an agile environment
\end{itemize}

\vspace{4pt}
\jobtitle{Graduate Research Intern — Deep Learning \& Neuroscience}{INSERM UMR 1231, NEUROGEMM — Dijon, France}{Feb. 2024 – Aug. 2024}
\begin{itemize}
  \item Built an automated \textbf{nnU-Net} segmentation pipeline for high-resolution 3D
        histological mouse brain volumes (Python, PyTorch)
  \item Preprocessed and managed large-scale 3D imaging datasets
  \item Tuned and evaluated model performance; collaborated with neuroscientists to
        validate biological accuracy
  \item Contributed to scientific documentation and internal presentations
\end{itemize}

\vspace{4pt}
\jobtitle{Full-Stack Developer (Full-time)}{Vision Eye Hospital — Dhaka, Bangladesh}{Dec. 2017 – Aug. 2022}
\begin{itemize}
  \item Designed and maintained a hospital ERP / HIMS solution deployed across \textbf{5 hospitals}
  \item Built modules for prescriptions, diagnostics, surgical workflows and patient records
  \item Stack: \textbf{Laravel}, \textbf{Vue.js}, \textbf{MySQL}; managed DevOps with Nginx/Apache on Linux
\end{itemize}

% ----
\section{Research Projects}

\textbf{3D Mouse Brain Segmentation} (nnU-Net, PyTorch)\newline
Automated pipeline for high-res histological 3D brain data; trained on GPU cluster. \href{https://github.com/taiaburbd}{\small[github]}

\vspace{3pt}
\textbf{CT Image Registration — Elastix + SimpleITK}\newline
Rigid and affine registration framework for multi-modal medical images. \href{https://github.com/taiaburbd}{\small[github]}

\vspace{3pt}
\textbf{3D Brain Tissue Segmentation (MRI)}\newline
U-Net architectures (TF + PyTorch) for WM / GM / CSF tissue delineation. \href{https://github.com/taiaburbd}{\small[github]}

\vspace{3pt}
\textbf{Skin Lesion Classification}\newline
Transfer learning with VGG16 \& ResNet50 on dermoscopic images; cross-validated. \href{https://github.com/taiaburbd}{\small[github]}

\vspace{3pt}
\textbf{Alzheimer's Classification — Multi-modal}\newline
Fused MRI features + gene expression data; SVM \& ensemble methods. \href{https://github.com/taiaburbd}{\small[github]}

\vspace{3pt}
\textbf{Retinal Image Analysis (2D)}\newline
Classical CV pipeline (thresholding, morphology) for hard exudate segmentation. \href{https://github.com/taiaburbd}{\small[github]}

% ----
\section{Software Products}

\textbf{AI-MIQA — Medical Image Quality Control Platform}\newline
\href{https://ai-miqa.com}{\texttt{ai-miqa.com}} — AI-powered platform for automated quality control and analysis
of medical images; enhances diagnostic accuracy for research and clinical use.

\vspace{3pt}
\textbf{Hospital Information Management System (HIMS)}\newline
Web-based ERP for healthcare; active in 5 hospitals (Bangladesh).
Stack: Laravel, Vue.js, MySQL.

% ============================================================
\switchcolumn
% ============================================================

% ---- RIGHT COLUMN ------------------------------------------

\section{Education}

\textbf{Erasmus Mundus Joint Master}\\
\textit{Medical Imaging \& Applications (MAIA)}\\
\textcolor{accent}{\small Sept. 2022 – Aug. 2024}\\[1pt]
{\small
Université de Bourgogne — Dijon, \textbf{France}\\
Università degli Studi di Cassino — Italy\\
Universitat de Girona — Spain\\[2pt]
\textit{Medical image segmentation \& registration,
deep learning, computer-aided diagnosis, surgical robotics, e-health.}
}

\vspace{5pt}
\textbf{MSc — Software Engineering}\\
{\small Tianjin University, China}

\vspace{4pt}
\textbf{BSc — Computer Science \& Engineering}\\
{\small Bangladesh University, Bangladesh}

% ----
\section{Technical Skills}

\begin{tabularx}{\linewidth}{@{}lX@{}}
\skill{ML / DL}{PyTorch, TensorFlow, Keras, Scikit-learn, nnU-Net, SimpleITK}
\skill{AI / LLM}{OpenAI API, Gemini API, LangChain (basics)}
\skill{Medical Img.}{Segmentation, Registration, CAD, 3D volume analysis}
\skill{Backend}{Python (FastAPI, Flask, Django), PHP (Laravel)}
\skill{Frontend}{Vue.js, React, TypeScript, JavaScript, jQuery}
\skill{DevOps / Cloud}{AWS (EC2, S3), Docker, CI/CD, Linux, Nginx}
\skill{Databases}{PostgreSQL, MySQL, SQLite}
\skill{Tools}{Git, REST API, Jupyter, Apache}
\end{tabularx}

% ----
\section{Languages}

\textbf{Bengali} — Native\\[1pt]
\textbf{English} — Upper-intermediate (\textbf{B2})\\[1pt]
\textbf{French} — Beginner (\textbf{A1–A2}, actively learning)

% ----
\section{Training \& Schools}

\textbf{17\textsuperscript{th} EXCITE Summer School}\\
\textit{Biomedical Imaging}\\
{\small ETH Zurich \& Univ. of Zurich, Switzerland \hfill \textcolor{accent}{Sept. 2023}}

\vspace{4pt}
\textbf{Winter School 2023}\\
{\small Università di Cassino, Italy \hfill \textcolor{accent}{Feb. 2023}}

% ----
\section{Target Roles (France)}

\begin{itemize}
  \item ML / AI Engineer — Medical Imaging, Health-Tech
  \item Fullstack Software Engineer (Python / Vue / React)
  \item R\&D Engineer — Computer Vision, Image Analysis
  \item DevOps / MLOps (Docker, AWS, CI/CD)
\end{itemize}

% ----
\section{ATS Keywords}

\vspace{1pt}
{\scriptsize\color{graytext}
Medical Imaging $\cdot$ 3D Segmentation $\cdot$ Deep Learning $\cdot$ PyTorch $\cdot$ nnU-Net $\cdot$ SimpleITK $\cdot$ Computer Vision $\cdot$ Python $\cdot$ FastAPI $\cdot$ Vue.js $\cdot$ React $\cdot$ Docker $\cdot$ AWS $\cdot$ CI/CD $\cdot$ REST API $\cdot$ SaaS $\cdot$ INSERM $\cdot$ Erasmus Mundus $\cdot$ MLOps
}

\end{paracol}

% ---- FOOTER ------------------------------------------------
\vspace{6pt}
{\color{rulecol}\hrule height 0.5pt}
\vspace{3pt}
\begin{center}
  \scriptsize\color{graytext}
  Paris, France — Open to on-site, hybrid or remote opportunities in France and Europe
\end{center}

\end{document}
